### 2019-05-11 papers/haskell19/4-generators.tex
NIT

Ideally, our aim is to be able to obtain random generators with a behavior
similar to the one presented for |Html| in Section \ref{sec:intro}.
%
If we take a closer look at its definition, there we can observe three factors
happening simultaneously:
%
\vspace{2pt}
\begin{CompactItemize}
\item We use QuickCheck's generation size to limit the depth of the generated
  values, reducing it by one on each recursive call of the local auxiliary
  function |gen|.
\item We differentiated between \emph{terminal} and \emph{non-terminal
    constructors}, picking only among terminal ones when we have reached the
  maximum depth (case |gen 0|).
\item We generate different constructions in a (possibly) different frequency.
\end{CompactItemize}
%
For the rest of this section, we will focus on modeling these aspects in our
modular framework, in such a way that does not compromise the compositionality
obtained so far.

>>>>

Ideally, our aim is to be able to obtain random generators with a behavior
similar to the one presented for |Html| in Section \ref{sec:intro}.
%
If we take a closer look at its definition, there we can observe three factors
happening simultaneously:
%
\vspace{2pt}
\begin{CompactItemize}
\item We use QuickCheck's generation size to limit the depth of the generated
  values, reducing it by one on each recursive call of the local auxiliary
  function |gen|.
\item We differentiate between \emph{terminal} and \emph{non-terminal
    constructors}, picking only among terminal ones when we have reached the
  maximum depth (case |gen 0|).
\item We generate different constructions in a (possibly) different frequency.
\end{CompactItemize}
%
For the rest of this section, we will focus on modeling these aspects in our
modular framework, in such a way that does not compromise the compositionality
obtained so far.
